---
title: "statistics-test.Rmd"
author: "Chett Rubenstein"
date: "May 17, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. The height (cm) of six random people in Williamsburg is sampled as the following: 178, 163, 168, 167, 170, 150
<pre>
a. Calculate the Five Number Summary: Min, First Quartile (Q1), Sample Median, Third Quartile (Q2), Maximum
b. Calculate the Sample Mean
c. Calculate the Interquartile Range (IQR)
d. Which, if any, of the observations are possible outliers?
e. Create a boxplot of the observations
f. Calculate the sample variance and sample standard deviation
</pre>

```{r question1}
height <- c(178, 163, 168, 167, 170, 150)
summary(height)
mean(height)
IQR(height)
outlier_values <- boxplot.stats(height)$out  # outlier values.
boxplot(height, main="Williamsburg Height", boxwex=0.1)
mtext(paste("Outliers: ", paste(outlier_values, collapse=", ")), cex=0.6)
var(height)
sd(height)
```

## 2. Group the following data types as either Metric, Non-Metric, or Inbetween (Metric implies we can calculate a "distance" between any two random observations), and categorize each one as either Continuous, Nominal/Categorical, Ordinal, or Interval/Discrete.
<pre>
i. All real numbers - Metric
ii. {First Place, Second Place, Third Place} - Non-Metric
iii. {Green, Blue, Yellow, Brown}
iv. Five point scale: 1, 2, 3, 4, 5
v. Ranking of attitudes on a 5 point scale: strongly disagree to strongly agree
</pre>

